---
title: "Developing Data Products"
author: "Kirram"
date: "November 21, 2015"
output: html_document
---
Disclaimer: this model was made up and does not repredsent real trends. 

The fields in the  allow a business owner to predict daily sales volumes based on weather data (humidity and temperature) and status of the shoe shop next door. Predictive model used - Random Forests. Please see Data.csv file for hisrotic (training data). Feel free to try different combinations of Temperature/Humidity/Shoe shop status. Enjoy :)

```{r}

library(shiny)
library(shinyapps)
library(caret)
library(party)
library(randomForest)
```

Reading data

```{r}
data1<-read.csv("Data.csv")
```

Training the model based on historic data using Random Forests
```{r}
train1<-train(Volume~Temperature+Humidity+Shop, data = data1, method="rf")
newdata<-read.csv("newdata.csv")
```

Creating Shiny Server file

```{r}
shinyServer(
  function(input,output){
    predicted<-reactive({
      output$inputValue<-renderPrint({input$Humidity})
      output$inputValue<-renderPrint({input$Temperature})
      output$inputValue<-renderPrint({input$ShopStatus})
      newdata$Temperature<-input$Temperature
      newdata$Humidity<-input$Humidity
      newdata$Shop<-input$Shop
      predict(train1, newdata=newdata)
    })
      output$Prediction<-renderPrint({paste(predicted())})
  }
)
```
